% !TeX root = ../sdc_regulations.tex
% Add the above to each chapter to make compiling the PDF easier for some editors.

\newpage
{\bf Changelog}
\\ \\{\bf Current Version: \\Version Draft \getVersion{}}
\\ \\Previous Versions: \\ No previous Versions

\newpage
{\bf Preface}
\\ \\ Welcome to the Swarm Drone Challenge! \\ \\
An evolution of the 2021 Deep Drone Challenge, the upcoming 2024 Swarm Drone Challenge will push the boundaries of drone technology as international teams present their creative and innovative algorithms. The focus on swarms opens new horizons for the fields of artificial intelligence and machine learning.

In the “Swarm Drone Challenge 2024”, participants develop solutions in which drones cooperate in a swarm and solve tasks together in competition. The “Swarm Drone Challenge 2024” is not only a stage for the competition, but also a platform for the exchange of ideas and techniques.
\newpage


{\bf Notes:
	\begin{itemize}
		\item Contents marked in \textcolor{red}{red} are still subject to change and should be seen as current estimations and placeholders.
		\item This whole document is still a work in progress. Some points may still be left empty.
		\item If you have any comments on specific regulations, for example, think that they are not required, are too strict or don't make sense, don't hesitate to contact fly@brigkair.digital.
		\item You are alway invited to contribute to this document by creating a pull request on github.
	\end{itemize}
}
\hspace{10mm}

\newpage
\newpage



