\section{Technical Regulations}

\subsection{Innovation Testbed}
\begin{enumerate}
	\item{\textcolor{red}{Open Interface Definitions for Hardware: TBD}}
	\item{\textcolor{red}{Open Interface Definitions for Software: TBD}}
	\item{\textcolor{red}{Open Interface Definitions for Network: TBD}}
\end{enumerate}

\subsection{Tagging}
\begin{enumerate}
	\item{No other drones must be physically harmed}
	\item{\textcolor{red}{Tagging could be implemented using detection in camera frame}}
\end{enumerate}

\subsection{Positioning}
\begin{enumerate}
	\item{\textcolor{red}{Indoor positioning system?}}
	\item{\textcolor{red}{mocap?}}
	\item{\textcolor{red}{slam?}}

\end{enumerate}

\subsection{Sense and Avoid}
\begin{enumerate}
	\item{Each drone should be capable of detecting static obstacles and other drones.}
	\item{Each drone must avoid collisions with other drones}
\end{enumerate}

\subsection{Emergency Shutoff and Kill Switch}
\begin{enumerate}
	\item{\textcolor{red}{Each drone must be equipped with a physical or virtual kill switch.}}
	\item{\textcolor{red}{Activation of the kill switch results in immediate landing or motor Shutoff}}
	\item{\textcolor{red}{One button to land whole swarm}}
\end{enumerate}

\subsection{Frequencies and communications}
\begin{enumerate}
	\item{\textcolor{red}{Rule 1}}
	\item{\textcolor{red}{Rule 2}}
	\item{\textcolor{red}{Rule 3}}
	\item{\textcolor{red}{Rule 4}}
\end{enumerate}

\subsection{Size and weight limits}
\begin{enumerate}
	\item{Below 25kg per drone}
	\item{The drone swarm must consist of no more than 8 drones}
	\item{The drone swarm must consist of more that 2 drones.}
\end{enumerate}

\subsection{Ground Control Station}
\begin{enumerate}
	\item{It is not required that the computing must be performed soley onboard.}
	\item{\textcolor{red}{The bahavior of individual drones can be either controlled by a single agent, which is aware of the global state or by one agent per drone.}}
\end{enumerate}

\subsection{Arbiter / Judge}
An Arbiter System to automate the rule enforcement process.
\begin{enumerate}

	\item{\textcolor{red}{Function 1 :TBD}}
	\item{\textcolor{red}{Function 2 :TBD}}
	\item{\textcolor{red}{Function 3 :TBD}}
	\item{\textcolor{red}{Function 4 :TBD}}
\end{enumerate}